---
title: "RWorksheet_Andica#3b"
author: "John Laurence Andica"
date: "2024-10-02"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. 1. Create a data frame using the table below.

a. Write the codes.
```{r}
library(readr)
myData <- data.frame(
  Respondents = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20),
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_School = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
myData
```
b. Describe the data. Get the structure or the summary of the data
```{r}
#The dataset consists of 20 respondents with a slight female majority, varying household sizes (3 to 11 persons), an average of 2 to 3 siblings in school, and fathers' occupations predominantly in three categories, indicating a balanced representation of household and familial structures.
str(myData)
```
c. Is the mean number of siblings attending is 5?
```{r}
mean_siblings <- mean(myData$Siblings_at_School)
mean_siblings
#No, the mean is 2.95
```
d. Extract the 1st two rows and then all the columns using the subsetting functions. Write the codes and its output.
```{r}
subset_data <- myData[1:2, ]
subset_data

```
e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r}
subset_data <- myData[c(3, 5), c(2, 4)]
subset_data

```
f. Select the variable types of houses then store the vector that results as types_houses. Write the codes.
```{r}
types_houses <- myData$Types_of_Houses
types_houses

```
g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.
```{r}
male_farmers_son <- subset(myData, Sex == 1 & Fathers_Occupation == 1)

male_farmers_son
```
h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.
```{r}
female_with_siblings = subset(myData, Sex == 2 & Siblings_at_School >= 5)
female_with_siblings
```
2. Write a R program to create an empty data frame. Using the following codes:
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
#The code outputs 0 observations or what we call row and 5 variables or what we call column.
```
3. Create a .csv file of this. Save it as HouseholdData.csv

a. Import the csv file into the R environment. Write the codes.
```{r}
my_Data <- read_csv("HouseholdData.csv")
my_Data
```
b. Convert the Sex into factor using factor() function and change it into integer.[Legend:
Male = 1 and Female = 2]. Write the R codes and its output.
```{r}
my_Data$Sex <- factor(my_Data$Sex, levels = c("Male", "Female"), labels = c(1, 2))
my_Data$Sex <- as.integer(my_Data$Sex)
my_Data$Sex
```
c. Convert the Type of Houses into factor and change it into integer. [Legend: Wood
= 1; Congrete = 2; Semi-Congrete = 3]. Write the R codes and its output.
```{r}
my_Data$Types_of_Houses <- factor(my_Data$Types_of_Houses, 
                            levels = c("Wood", "Congrete", "Semi-congrete"),
                            labels = c(1, 2, 3))
my_Data$Types_of_Houses <- as.integer(my_Data$Types_of_Houses)
my_Data$Types_of_Houses

```
d. On father’s occupation, factor it as Farmer = 1; Driver = 2; and Others = 3. What
is the R code and its output?
```{r}
fathers_occupation_vector <- my_Data$Fathers_Occupation
fathers_occupation_factor <- factor(fathers_occupation_vector,
                                    levels = c(1, 2, 3),
                                    labels = c("Farmer", "Driver", "Others"),
                                    exclude = NULL)
fathers_occupation_character <- as.character(fathers_occupation_factor)
fathers_occupation_character
```

e. Select only all females respondent that has a father whose occupation is driver. Write
the codes and its output.
```{r}
female_drivers <- my_Data[my_Data$Sex == 2 & fathers_occupation_character == "Driver", ]
female_drivers
```
f. Select the respondents that have greater than or equal to 5 number of siblings attending
school. Write the codes and its output.

```{r}
more_siblings <- my_Data[my_Data$Siblings_at_School >= 5, ]
more_siblings

```


